---
title: "Finding The Break Point"
author: "Group 3: Charles Manzoni, Shoko Wadano, Camila Baquero, Edward Jerse, Juan D. Alvarez"
date: "2/27/2020"
output: word_document
---
# PROBLEM DESCRIPTION
Our team wanted to determine if we could use machine learning to make predictions about the outcome of tennis matches. Specifically, we wanted to know if we could accurately predict who will win a given match, and devise a betting strategy to profit from these predictions. 

# DATA OVERVIEW
## Data Sources
We pulled data from two primary sources for this project:

1. The first contains historical information on tennis matchups, from 2012-2016 and can be found on kaggle. This was the primary dataset used in all analysis: https://www.kaggle.com/gmadevs/atp-matches-dataset
2. The second contains historical betting odds for certain matches. This data was used as a test sample to analyze various betting strategies applied with out model output. Data can be found at https://www.oddsportal.com/results/#tennis

The data from source 1, however, was on a match-by-match bases, and did not provide many variables that would be available to predict the outcome of that match before the match occurred. Instead, the data contained stats about the match itself, such as who won, how many aces a player had, how many break points a player saved, etc. To create a more useful set to use to predict the outcome of future matches, this original dataset was manipulated in SQL. The manipulations were primarily to calculate various statistics for each player (e.g. win %, average opponent rank, average opponent height, average aces, average break points saved, etc) over given periods of history leading up to each match. The periods selected were:

1. A player's last 20 matches
2. A player's last 20 matches on the surface type to be played on
2. A player's last 50 matches
3. A player's entire previous season and all matches leading up to the one in question in the current season

The last SQL manipulation performed was then to calculate the difference between opponents for each of the various metrics. As an example:
If Federer were playing Nadal, we would look at all 20 of Federers last matches, and calculate the statistics for him (e.g. win percent, average opponent rank, average opponent height, average aces, etc.). We would do the same for Nadal. We would then calculate the difference between these two mettrics so that R can analyze the matchup between the two players rather than have to look at two different fields per statistic to understand the matchup.

## Variable Definition Table
Below are selected columns in the primary dataset, which was dataset #1 (tennis match stats) after the SQL manipulation. Only select columns are shown for the calculated metrics, using only those calculated for the last 20 matches. Note that the exact same columns are also present for the previous 50 matches as well as the previous season:

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
table <- "
|Variable Name                                 |Definition                                                                 |
|----------------------------------------------|---------------------------------------------------------------------------|
|tourney_id                                    |uid for tournament                                                         |
|match_num                                     |uid for match                                                              |
|player_id                                     |uid for player                                                             |
|opp_id                                        |uid for opponent                                                           |
|tourney_date                                  |date of tournament                                                         |
|surface                                       |clay, grass, or hard                                                       |
|tourney_level                                 |A, B, C, etc.                                                              |
|best_of                                       |3 or 5 sets                                                                |
|player_name                                   |name of player                                                             |
|player_seed                                   |player seed in tournament                                                  |
|matchup_hand                                  |player-opponent dominant hand                                              |
|matchup_ht_diff                               |player height - opponent height                                            |
|matchup_age_diff                              |player age - opponent age                                                  |
|matchup_rank_diff                             |player rank - opponent rank                                                |
|matchup_rankpoints_diff                       |player rankpoints - opponent rankpoints                                    |
|opp_name                                      |opponent name                                                              |
|opp_seed                                      |opponent seed in tournament                                                |
|matchup_perc_matchesSurface_last20            |difference in the percentage of the last 20 matches played on that surface |
|matchup_win_perc_last20_diff                  |difference in win percentage                                               |
|matchup_avg_rank_last20_diff                  |difference in average rank                                                 |
|matchup_avg_rankPoints_last20_diff            |difference in average rankpoints                                           |
|matchup_avg_acePerSet_last20_diff             |difference in average aces per set                                         |
|matchup_avg_df_perSet_last20_diff             |difference in average double faults per set                                |
|matchup_avg_svpt_perSet_last20_diff           |difference in average service points per set                               |
|matchup_avg_1stIn_perSet_last20_diff          |difference in average number of 1st serves in per set                      |
|matchup_avg_1stWon_perSet_last20_diff         |difference in average number of 1st serves won per set                     |
|matchup_avg_2ndWon_perSet_last20_diff         |difference in average number of 2nd serves won per set                     |
|matchup_avg_svGms_perSet_last20_diff          |difference in average number of service games per set                      |
|matchup_avg_bpSaved_perSet_last20_diff        |difference in average number of break points saved per set                 |
|matchup_avg_bpFaced_perSet_last20_diff        |difference in average number of break points faced per set                 |
|matchup_perc_bpSaved_last20_diff              |difference in percentage of break points saved                             |
|matchup_avg_opp_ht_last20_diff                |difference in average height of opponents faced                            |
|matchup_avg_opp_age_last20_diff               |difference in average age of opponents faced                               |
|matchup_perc_opp_RH_last20_diff               |difference in percentage of RH-dominant opponents faced                    |
|matchup_avg_opp_rank_last20_diff              |difference in average rank of opponents faced                              |
|matchup_avg_opp_rankpoints_last20_diff        |difference in average rankpoints of opponents                              |
|matchup_avg_acePerSet_allowed_last20_diff     |difference in average aces allowed per set                                 |
|matchup_avg_df_perSet_allowed_last20_diff     |difference in average double faults allowed per set                        |
|matchup_avg_svpt_allowed_perSet_last20_diff   |difference in average service points allowed per set                       |
|matchup_avg_1stIn_allowed_perSet_last20_diff  |difference in average first serves allowed in per set                      |
|matchup_avg_1stWon_allowed_perSet_last20_diff |difference in average number of points lost on 1st serves per set          |
|matchup_avg_2ndWon_allowed_perSet_last20_diff |difference in average number of points lost on 2nd serves per set          |
|matchup_avg_svGms_allowed_perSet_last20_diff  |difference in average number of service games faced per set                |
|matchup_avg_bpSaved_allowed_perSet_last20_diff|difference in average number of break points lost per set                  |
|matchup_avg_bpFaced_allowed_perSet_last20_diff|difference in average number of break points forced per set                |
|matchup_perc_bpSaved_allowed_last20_diff      |difference in percentage of break points lost                              |
|matchup_avg_spreadPerSet_last20_diff          |difference in average spread (games) per set                               |
|matchup_std_spreadPerSet_last20_diff          |difference in stdev of spread (games) per set                              |
|matchup_avg_minutesPerSet_last20_diff         |difference in averagematch length                                          |
|player_won_ind (dependent Q1 & Q2)            |1 if the 'player' won, 0 if 'opponent' won                                 |
|player_games_spread                           |player games won - opponent games won                                      |
|minutes (dependent Q3)                        |length of match                                                            |
"
cat(table)
```


Here are the variables for dataset #2 (the historical odds):
```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
table <- "
|Variable Name|	Definition                                |
|-------------|	------------------------------------------|
|tourney_id   |	uid for tournament                        |
|match_num    |	uid for match                             |
|tourney_date |	tournament date                           |
|tourney_name |	tournament name                           |
|surface      |	clay, grass, or hard                      |
|year         |	year of tournament                        |
|player_name  |	player name                               |
|opp_name     |	oppoonent name                            |
|player_LN    |	player last name                          |
|Opp_LN       |	opponent last name                        |
|player_odds  |	payoff on a moneyline bet on the player   |
|opp_odds     |	payoff on a moneyline bet on the opponent |
"
cat(table)
```


# ANALYSIS AND FINDINGS
First, we need to conduct some initial data cleansing before we could run any regressions to answer the three questions
```{R, echo=TRUE, eval=TRUE, results='hide'}
#Load Required Packages
library(ggplot2)
library(GGally)
library(lmtest)
library(olsrr)
library(fpp2)
library(faraway)
library(usdm)
library(car)
library(leaps)
library(glmnet)
library(fastDummies)
library(Hmisc)
library(caret)
library(MASS)
library(mgcv)
library(dplyr)
```
```{R, echo=TRUE, eval=TRUE}
#READ DATA
tennis <- read.csv('08_FinalData.csv')
#Remove variables unique to a match (names, ids, tourney dates, outcomes, etc.)
colnames(tennis)
tennis1 <- select(tennis,-c(tourney_id, match_num, player_id, opp_id, tourney_date, player_name, opp_name))
tennis1 <- select(tennis1,-c(minutes, player_games_spread)) #remove "minutes" and "games spread" since they are the outcome of a match

#Deal with Fields with NA's
tennis1 <- select(tennis1,-c(player_seed, opp_seed)) #removed the player and opp seed since many nulls and not thought to be too important

tennis1$matchup_ht_diff <- impute(tennis1$matchup_ht_diff, mean) #replace nulls with the mean
tennis1$matchup_age_diff <- impute(tennis1$matchup_age_diff, mean) #replace nulls with the mean
#create dummies

tennis2 <- data.frame(model.matrix(~. , data=tennis1)) #removes a few rows with null values
dim(tennis1)
dim(tennis2) #Note some records are lost if there were null values when creating the model matrix
```
```{R, echo=TRUE, eval=TRUE}
#Examine the Data
hist(tennis2$player_won_ind)
```

We can see that of the matches, we have about 50% of them won by "player" and 50% of them won by "opponent". This makes sense since the "player" and "opponent" were randomized.
```{R, echo=TRUE, eval=FALSE}
#remove fields that are multicollinear
good_vars <- vifstep(tennis2, th=5) 
good_vars
```
```{R, echo=TRUE, eval=TRUE}
tennis3 <- tennis2[-1] #remove intercept
tennis3 <- select(tennis3, -c(surfaceClay,matchup_avg_bpFaced_perSet_last50_diff,matchup_avg_bpFaced_allowed_perSet_last50_diff,matchup_avg_bpFaced_perSet_lastSeason_diff,matchup_avg_1stWon_perSet_last50_diff,matchup_avg_bpFaced_allowed_perSet_lastSeason_diff,matchup_avg_bpFaced_perSet_last20_diff,matchup_avg_1stWon_allowed_perSet_last50_diff,matchup_avg_bpFaced_allowed_perSet_last20_diff,matchup_avg_svpt_perSet_last50_diff,matchup_avg_rankPoints_last20_diff,matchup_avg_svpt_allowed_perSet_last50_diff,matchup_avg_1stWon_perSet_last20_diff,matchup_avg_svGms_perSet_last50_diff,matchup_avg_bpFaced_perSet_last20Surface_diff,matchup_avg_svpt_perSet_lastSeason_diff,matchup_avg_bpFaced_allowed_perSet_last20Surface_diff,matchup_avg_svpt_allowed_perSet_last20_diff,matchup_avg_svGms_allowed_perSet_lastSeason_diff,matchup_avg_1stWon_perSet_lastSeason_diff,matchup_avg_1stWon_allowed_perSet_lastSeason_diff,matchup_avg_spreadPerSet_last50_diff,matchup_avg_svpt_perSet_last20Surface_diff,matchup_avg_svGms_allowed_perSet_last20_diff,matchup_avg_acePerSet_last50_diff,matchup_avg_svpt_allowed_perSet_last20Surface_diff,matchup_avg_rankPoints_last50_diff,matchup_avg_1stWon_allowed_perSet_last20_diff,matchup_avg_1stIn_perSet_last20_diff,matchup_avg_svGms_perSet_last20Surface_diff,matchup_avg_svpt_allowed_perSet_lastSeason_diff,matchup_avg_1stWon_perSet_last20Surface_diff,matchup_avg_1stWon_allowed_perSet_last20Surface_diff,best_of,matchup_avg_svGms_allowed_perSet_last50_diff,matchup_avg_rankPoints_last20Surface_diff,matchup_avg_spreadPerSet_lastSeason_diff,matchup_avg_svGms_perSet_lastSeason_diff,matchup_avg_1stIn_perSet_last50_diff,matchup_avg_acePerSet_lastSeason_diff,matchup_avg_spreadPerSet_last20_diff,matchup_win_perc_last50_diff,matchup_avg_svpt_perSet_last20_diff,matchup_avg_2ndWon_perSet_last50_diff,matchup_avg_svGms_allowed_perSet_last20Surface_diff,matchup_avg_rank_last50_diff,matchup_avg_df_perSet_last50_diff,matchup_avg_acePerSet_last20_diff,matchup_avg_svGms_perSet_last20_diff,matchup_avg_bpSaved_perSet_lastSeason_diff,matchup_avg_spreadPerSet_last20Surface_diff,matchup_avg_acePerSet_allowed_last50_diff,matchup_avg_1stIn_allowed_perSet_lastSeason_diff,matchup_handRR,matchup_avg_bpSaved_allowed_perSet_last50_diff,matchup_rankpoints_diff,matchup_perc_bpSaved_last50_diff,matchup_avg_opp_rankpoints_last50_diff,matchup_avg_2ndWon_allowed_perSet_last50_diff,matchup_avg_rank_last20_diff,matchup_win_perc_lastSeason_diff,matchup_avg_2ndWon_perSet_lastSeason_diff,matchup_avg_1stIn_perSet_last20Surface_diff,matchup_avg_bpSaved_perSet_last20_diff,matchup_avg_minutesPerSet_last50_diff,matchup_std_spreadPerSet_last50_diff,matchup_avg_opp_rank_last50_diff,matchup_avg_df_perSet_lastSeason_diff,matchup_perc_bpSaved_allowed_last20_diff,matchup_avg_1stIn_allowed_perSet_last20_diff,matchup_avg_acePerSet_allowed_lastSeason_diff,matchup_total_matches_last50_diff,matchup_avg_minutesPerSet_last20Surface_diff))
```

## Analysis: Can we accurately predict the winner of a tennis match, and use that model to devise a winning betting strategy?

### Split into training data (2014, 2015) and test data (2016)
```{R, echo=TRUE, eval=TRUE}
tennis3$rowid <- rownames(tennis3)
year_data <-  data.frame(cbind(rowid=rownames(tennis),tennis[5]))
year_data$year <- sapply(year_data$tourney_date, function(x) substr(x,1,4))
year_data <- year_data[-2]
tennis3 <- merge(tennis3, year_data, by='rowid') #bring in the year
tennis3_train <- tennis3[tennis3$year=='2014'|tennis3$year=='2015',]
tennis3_test <- tennis3[tennis3$year=='2016',]

tennis3_train <- tennis3_train[-85] #remove year
tennis3_train <- tennis3_train[-1] #remove rowid
tennis3_test <- tennis3_test[-85] #remove year
tennis3_test <- tennis3_test[-1] #remove rowid
```
### Logistic Regression

Run a full regression with 'clean' variables, and perform stepwise feature selection
```{R, echo=TRUE, eval=FALSE}
log1 <- glm(player_won_ind ~ ., data=tennis3_train, family=binomial) %>%
  stepAIC(trace=FALSE)
summary(log1)
1 - log1$deviance/log1$null.deviance #0.168 - may not be that bad
```
Build a second regression w significant vars (note this was done stepwise, removing one non-significant variable at a time) result is below:
```{R, echo=TRUE, eval=TRUE}
log2 <- glm(player_won_ind ~ tourney_levelD + tourney_levelG + 
    matchup_ht_diff + matchup_age_diff + matchup_rank_diff +  
    matchup_avg_rankPoints_lastSeason_diff +  
    matchup_avg_opp_rankpoints_lastSeason_diff + matchup_avg_bpSaved_allowed_perSet_lastSeason_diff + 
    matchup_win_perc_last20_diff + matchup_avg_2ndWon_perSet_last20_diff + 
    matchup_avg_opp_rankpoints_last20_diff + matchup_avg_acePerSet_allowed_last20_diff + 
    matchup_avg_bpSaved_perSet_last50_diff + matchup_total_matches_last20Surface_diff + 
    matchup_avg_acePerSet_last20Surface_diff + matchup_avg_2ndWon_perSet_last20Surface_diff + 
    matchup_avg_bpSaved_perSet_last20Surface_diff + matchup_perc_bpSaved_last20Surface_diff + 
    matchup_avg_acePerSet_allowed_last20Surface_diff + 
    matchup_avg_bpSaved_allowed_perSet_last20Surface_diff + matchup_perc_bpSaved_allowed_last20Surface_diff, family = binomial, 
    data = tennis3_train)
summary(log2)
1 - log2$deviance/log2$null.deviance
```
Next, we will attempt a prediction of both the training and the test set, to determine the model's accuracy
```{R, echo=TRUE, eval=TRUE}
result_train <- predict(log2, tennis3_train, type="response")
result_test <- predict(log2, tennis3_test, type="response")
plot(result_train)
plot(result_test)
```
Next, we will convert the result to orignal factor level: "win" or "loss"
```{R, echo=TRUE, eval=TRUE}
tennis3_train$pred[result_train>0.5] <- "win"
tennis3_train$pred[result_train<=0.5] <- "loss"
tennis3_train$pred <- as.factor(tennis3_train$pred)
tennis3_train$actual <- ifelse(tennis3_train$player_won_ind == 1, "win", "loss")
tennis3_train$actual <- as.factor(tennis3_train$actual)
tennis3_train <- cbind(tennis3_train, result_train)
#Test Set
tennis3_test$pred[result_test>0.5] <- "win"
tennis3_test$pred[result_test<=0.5] <- "loss"
tennis3_test$pred <- as.factor(tennis3_test$pred)
tennis3_test$actual <- ifelse(tennis3_test$player_won_ind == 1, "win", "loss")
tennis3_test$actual <- as.factor(tennis3_test$actual)
tennis3_test <- cbind(tennis3_test, result_test)
```
Create a confusion matrix for the training and test subsets
```{R, echo=TRUE, eval=TRUE}
conf_table_train <- confusionMatrix(tennis3_train$pred, tennis3_train$actual, positive="win")
conf_table_train
conf_table_test <- confusionMatrix(tennis3_test$pred, tennis3_test$actual, positive="win")
conf_table_test
```
We can see that the output appears to give good results with accuracies around 68%. 


### Prediction Using KNN Model


### Prediction Using Neural Net (ANN) Model - CHARLIE TO COMPLETE


### Prediction Using Support Vector Maching (SVM) Model


### Prediction Using Decision Tree Model


### Prediction Using Random Forest Model


### Prediction Using Ensemble Model


## Evaluating / Comparing the Models - CHARLIE TO COMPLETE

## Analyzing Betting Strategies  (CHARLIE TO CLEAN UP AFTER SECTIONS ABOVE COMPLETE)
From here, we will bring in the historical odds for a random sample of matches in 2016, and test various betting strategies to determing if this model can be profitable
```{R, echo=TRUE, eval=TRUE}
#bring in odds data to evaluate
odds <- read.csv('22_MatchData_OddsData.csv')
odds$match_key <- paste(odds$tourney_id, odds$match_num,sep='||')
#create output df with only relevant columns
predictions <- data.frame(cbind(rowid = rownames(tennis_logreg_test),tennis_logreg_test[81:84]))
orig_key_data <- data.frame(cbind(rowid=rownames(tennis),tennis[1:2]))
predictions <- merge(orig_key_data, predictions, by="rowid")
predictions$match_key <- paste(predictions$tourney_id,predictions$match_num,sep='||')
#merge in the odds data
predictions <- merge(predictions, odds, by='match_key')
```
Strategy 1: Calculate payoff if you were to bet $100 on each match, betting on the player predicted to win:
```{R, echo=TRUE, eval=TRUE}
#Calculate the payoffs for $100 bets on the 'player' and 'opponent' if the bets were to win
predictions$betplayer_payoff <- sapply(predictions$player_odds, function(x) if (x>0) {x} else {-100*100/x})
predictions$betopp_payoff <- sapply(predictions$opp_odds, function(x) if (x>0) {x} else {-100*100/x})
#Define function for the payoff of the bets on each match
bet_all_payoff <- function(prediction, actual, player_payoff, opp_payoff)
{
  if ((prediction == 'loss' & actual == 'win') || (prediction=='win' & actual=='loss'))
  {
    return(-100)
  }
  else if (prediction =='loss')
  {
    return(opp_payoff)
  }
  else
  {
    return(player_payoff)
  }
}

predictions$bet_all_payoff <- mapply(bet_all_payoff, predictions$pred, predictions$actual, predictions$betplayer_payoff, predictions$betopp_payoff)
paste('total return on placing bets on all matches is',toString(sum(predictions$bet_all_payoff)/(100*nrow(predictions))))
paste('Total Bet: ',toString(100*nrow(predictions)))
paste('Total Gains: ',toString(sum(predictions$bet_all_payoff)))
```
Strategy 2: Bet only on matches we are confident in (using 75% win probability cutoff)
```{R, echo=TRUE, eval=TRUE}
bet_confidence_payoff <- function(cutoff, player_winprob, prediction, actual, player_payoff, opp_payoff)
{
  if (player_winprob<cutoff & player_winprob > 1-cutoff)
  {
    return(0)
  }
  else  if ((prediction == 'loss' & actual == 'win') || (prediction=='win' & actual=='loss'))
  {
    return(-100)
  }
  else if (prediction =='loss')
  {
    return(opp_payoff)
  }
  else
  {
    return(player_payoff)
  }
}

bet_confidence_count <- function(cutoff, player_winprob, prediction, actual, player_payoff, opp_payoff)
{
  if (player_winprob<cutoff & player_winprob > 1-cutoff)
  {
    return(0)
  }
  else
  {
    return(1)
  }
}

predictions$bet_confidence_payoff <- mapply(bet_confidence_payoff, .75, predictions$result, predictions$pred, predictions$actual, predictions$betplayer_payoff, predictions$betopp_payoff)
predictions$bet_confidence_count <- mapply(bet_confidence_count, .75, predictions$result, predictions$pred, predictions$actual, predictions$betplayer_payoff, predictions$betopp_payoff)

paste('total return on placing bets on confident matches is',toString(sum(predictions$bet_confidence_payoff)/(100*sum(predictions$bet_confidence_count))))
paste('Total Bet: ',toString(100*sum(predictions$bet_confidence_count)))
paste('Total Gains: ',toString(sum(predictions$bet_confidence_payoff)))
```
Strategy 3: Bet only on matches with positive expected value, based on p(win) and payoff
```{R, echo=TRUE, eval=TRUE}
bet_expected_payoff <- function(player_winprob, actual, player_payoff, opp_payoff)
{
  if ((player_winprob*player_payoff)+(1-player_winprob)*(-100)<0 & (player_winprob*(-100))+(1-player_winprob)*opp_payoff<0)
  {
    return(0)
  }
  else  if (((player_winprob*(-100))+(1-player_winprob)*opp_payoff>0 & actual == 'win') || ((player_winprob*player_payoff)+(1-player_winprob)*(-100)>0 & actual=='loss'))
  {
    return(-100)
  }
  else if ((player_winprob*player_payoff)+(1-player_winprob)*(-100)>0)
  {
    return(player_payoff)
  }
  else
  {
    return(opp_payoff)
  }
}

bet_expected_count <- function(player_winprob, actual, player_payoff, opp_payoff)
{
  if ((player_winprob*player_payoff)+(1-player_winprob)*(-100)<0 & (player_winprob*(-100))+(1-player_winprob)*opp_payoff<0)
  {
    return(0)
  }
  else
  {
    return(1)
  }
}

predictions$bet_expected_payoff <- mapply(bet_expected_payoff, predictions$result, predictions$actual, predictions$betplayer_payoff, predictions$betopp_payoff)
predictions$bet_expected_count <- mapply(bet_expected_count, predictions$result, predictions$actual, predictions$betplayer_payoff, predictions$betopp_payoff)

paste('total return on placing bets on high expected val matches is',toString(sum(predictions$bet_expected_payoff)/(100*sum(predictions$bet_expected_count))))
paste('Total Bet: ',toString(100*sum(predictions$bet_expected_count)))
paste('Total Gains: ',toString(sum(predictions$bet_expected_payoff)))
```
Strategy 4: Bet only on matches with positive expected value, and with a probability above a certain confidence.  Note this was devised because there were a number of matches in strategy 3 that we were bettiing on because there was a very low probability of winning, but a very high payoff. These did not seem like good bets
```{R, echo=TRUE, eval=TRUE}
bet_expected_conf_payoff <- function(player_winprob, cutoff, actual, player_payoff, opp_payoff)
{
  if (((player_winprob*player_payoff)+(1-player_winprob)*(-100)<0 & (player_winprob*(-100))+(1-player_winprob)*opp_payoff<0))
  {
    return(0)
  }
  else  if (((player_winprob*(-100))+(1-player_winprob)*opp_payoff>0 & player_winprob<(1-cutoff) & actual == 'win') || ((player_winprob*player_payoff)+(1-player_winprob)*(-100)>0 &  player_winprob > cutoff & actual=='loss'))
  {
    return(-100)
  }
  else if ((player_winprob*player_payoff)+(1-player_winprob)*(-100)>0 & player_winprob > cutoff)
  {
    return(player_payoff)
  }
  else if ((player_winprob*(-100))+(1-player_winprob)*opp_payoff>0 & player_winprob<(1-cutoff))
  {
    return(opp_payoff)
  }
  else
  {
    return(0)
  }
}

bet_expected_conf_count <- function(player_winprob, cutoff, actual, player_payoff, opp_payoff)
{
  if (((player_winprob*player_payoff)+(1-player_winprob)*(-100)>0 & player_winprob > cutoff) || ((player_winprob*(-100))+(1-player_winprob)*opp_payoff>0) & (1-player_winprob)>cutoff)
  {
    return(1)
  }
  else
  {
    return(0)
  }
}


predictions$bet_expected_conf_payoff <- mapply(bet_expected_conf_payoff, predictions$result, .75, predictions$actual, predictions$betplayer_payoff, predictions$betopp_payoff)
predictions$bet_expected_conf_count <- mapply(bet_expected_conf_count, predictions$result, .75, predictions$actual, predictions$betplayer_payoff, predictions$betopp_payoff)

paste('total return on placing bets on high expected val, high confidence matches is',toString(sum(predictions$bet_expected_conf_payoff)/(100*sum(predictions$bet_expected_conf_count))))
paste('Total Bet: ',toString(100*sum(predictions$bet_expected_conf_count)))
paste('Total Gains: ',toString(sum(predictions$bet_expected_conf_payoff)))
```
As we can see, strategy 4 appears to give the best returns. To understand the strategy better, we will look at the cash position over time:
```{R, echo=TRUE, eval=TRUE}
predictions$tourney_date <- sapply(predictions$tourney_date, function(x) toString(x))
predictions$date <- as.Date(predictions$tourney_date, format='%Y%m%d')
predictions <- predictions[order(predictions$date),]
predictions$bet_expected_conf_cumsum <- cumsum(predictions$bet_expected_conf_payoff)
ggplot(predictions) +
  geom_point(aes(x=date, y=bet_expected_conf_cumsum))+
  geom_line(aes(x=date, y=bet_expected_conf_cumsum))+
  geom_smooth(aes(x=date, y=bet_expected_conf_cumsum), method='loess')

```
As we can see, this strategy appears to be very attractive, as the cash position trends upward fairly constantly, and there are few instances when cash position is negative

